\subsection{Integration of forms}
moving on to integration of diff forms

for $k$-forms on $\bR^{k}$, if $f$ has cpt sppt in $U$, we can defn:
\begin{equation*}
	\int_{U}\omega \ = \ \int_{\bR^{k}}f(x_{1},\dots,x_{k})\di x_{1}\cdots\d x_{k}
\end{equation*}
from last time, we see that $\int_{F(U)}\omega=\pm\int_{U}F^{*}\omega$ by cov, where
$F:U\gto F(U)$ diffeo.

for $k$-forms on a $k$-mfld:
sps $\omega\in\Omega^{k}(M^{k})$ has cpt sppt.
then we can find charts $U_{1},\dots,U_{r}$ st $\omega$ supp on $\bigcup U_{i}$, and
can write:
\begin{equation*}
	\omega=\rho_{1}\omega+\dots +\rho_{r}\omega
\end{equation*}
where $\rho_{i}:M\gto\bR$ is a parition of unity w sppt $U_{i}$. then by defn:
\begin{equation*}
	\int_{M}\omega \ = \ \sum_{i=1}^{r}\int_{\vphi_{i}(U_{i})}(\vphi_{i}^{-1})^{*}(\rho_{i}\omega)
\end{equation*}
where we choose $\vphi_{i}$'s to have compat orientations, ie
$\det(T(\vphi_{i}\circ\vphi_{j}^{-1}))>0$ for all $i,j$.

\lecdate{Lec 21 - Mar 26 (Week 11)}
last time, we talked abt integrating $k$-forms on $k$-mflds.
an important note is that the defn from last time is indep of coords.
we can do sth similarly for all forms.

\begin{defn}
	given $\omega\in\Omega^{k}(M^{m})$, $k$-dim'l oriented submfld $\iota:S\ito M$,
	we can define:
	\begin{equation*}
		\int_{S}\omega \ = \ \int_{S}\iota^{*}\omega
	\end{equation*}
	note on the left, $S\subseteq M$ and $\omega\in\Omega^{k}(M)$, but
	on the right, $S$ is a mfld in and of itself and $\iota^{*}\omega\in\Omega^{k}(S)$.
\end{defn}
goal for tdy: prove generalized stokes (we have 30 mins left in class).
here's the statement.

\begin{thm}[title=Generalized Stokes' Theorem]
	let $A\subseteq M^{m}$ be a \textit{bounded region} with \textit{boundary} $\p A$.
	then for any $\alpha\in\Omega^{m-1}(M)$ with $\supp(\alpha)\cap A$ cpt, we have:
	\begin{equation*}
		\int_{\p A}\omega \ = \ \int_{A}\d\omega
	\end{equation*}
\end{thm}
remark: $M$ may be a submfld of sth higher-dim!
other remark: we literally havent talked abt bdries lmao

\begin{xmp} \vspace{-0.2in}
	\begin{enumerate}[i)]
		\item sps $\alpha\in\Omega^{2}(\bR^{3})$, $A$ some bounded region in $\bR^{3}$.
			then this yields the divergence theorem.
		\item sps $\alpha\in\Omega^{1}(\bR^{3})$, $A$ some bounded surface in $\bR^{3}$.
			then this yields the classical stokes thm.
		\item sps $\alpha\in\Omega^{0}(M)=C^{\infty}(M)$.
			then this yields the fundamental thm of calculus.
	\end{enumerate}
\end{xmp}
gave 2 exs w pictures. oh well

\begin{crll}
	(more of a special case) if $\alpha$ closed, then:
	\begin{equation*}
		\int_{\p A}\alpha \ = \ 0
	\end{equation*}
\end{crll} \

\begin{defn}
	sps $M$ oriented.
	we say $D\subseteq M$ is a \textbf{region with smooth boundary} if
	$\ex f:C^{\infty}(M)$ with 0 as a reg val and $D=f^{-1}(t\leq0)$.
	we write $\p D=f^{-1}(0)$ and $\trm{int}(D)=f^{-1}(t<0)$.
\end{defn}
fix a special atlas covering $D$:
\begin{itemize}
	\item cvr $\p D$ by submfld charts $(U,\vphi)$ compat w orientation of $M$, ie:
		\begin{equation*}
			\vphi(U\cap\p D) \ = \ \vphi(U)\cap\set{x_{1}=0} \qquad
			\vphi(U\cap\trm{int}D) \ = \ \vphi(U)\cap\set{x_{1}<0}
		\end{equation*}
		after possibly flipping sign of $x_{1}$
	\item cvr interior by more oriented charts
\end{itemize}
this gives an oriented atlas on $D$.

\begin{prop}
	when restricting to $\set{x_{1}=0}$, we get an oriented atlas on $\p D$
\end{prop} \

\begin{pf}
	let $\tau:\vphi_{i}(U_{i}\cap U_{j})\gto\vphi_{j}(U_{i}\cap U_{j})$ be
	the transition map.
	given $x=(0,x_{2},\dots,x_{m})$, consider $T_{x}\tau$:
	the top left is $>0$ since ``away from $D$" is preserved, the rest of
	the first row is 0 [cz bdry is preserved? idk], and ignoring the
	first column, the remaining matrix is made up of the jacobian of
	the transition map btwn charts on $\p D$.

	we know $\det T_{x}\tau>0$, so $\det$(that other thing) is +ve, so the atlas
	$\left(U\big\rvert_{\p D},\vphi\big\rvert_{\p D}\right)$ is oriented.
\end{pf}
note: the orientation we put on $\p D$ is engineered to avoid a minus sign.
