\subsection{Poincare(-Hopf) Theorem}

we know what winding number is. note that:
\begin{enumerate}[1)]
	\item $\gamma(t)=(\cos(2\pi nt),\sin(2\pi nt))$ has winding num $n$
	\item winding num is inv under deformations that stay in the punctured plane.
\end{enumerate}
number 2 suggests we can define $\int_{\gamma}$(closed form).

\begin{defn}
	the \textbf{winding number} of a loop $\gamma$ is given by:
	\begin{equation*}
		w(\gamma) \ = \ \int_{S^{1}}\gamma^{*}\left(\frac{\d\theta}{2\pi}\right)
	\end{equation*}
\end{defn}
note $\theta$ is as in polar coords, but $\theta$ is not a smooth fn
$\bR^{2}\sm\set{0}\gto\bR$, so $\d\theta$ is not exact.

compute: if $x=r\cos\theta,r^{2}=x^{2}+y^{2}$, then:
\begin{equation*}
	\d x \ = \ -r\sin\theta\d\theta+\d r\cos\theta \qquad
	2r\d r \ = \ 2x\d x+2y\d y
\end{equation*}
therefore:
\begin{equation*}
	\d\theta \ = \ \frac{x\d y-y\d x}{x^{2}+y^{2}}
\end{equation*}
check its closed.
this satisfies 1) by computation, and 2) by properties of closed forms.

moreover:
\begin{enumerate}[1)]
	\item $w(\gamma)\in\bZ$
	\item two loops can be deformed into each other iff they have the same winding num
	\item joining loops by a path results in a loop whose winding num is the
		sum of the others' winding nums
\end{enumerate}

\begin{thm}[title=Poincare's Theorem]
	let $\Sigma$ be cpt oriented surface w $\p$, $X$ VF on $\Sigma$ w \textit{isolated zeroes}
	(or equivalently by cptness, finitely many).
	let $\cl{C}$ denote the connected components of the bdry (ie circles).
	then:
	\begin{equation*}
		\sum_{\trm{0's}}\trm{index}_{p}(X) - \sum_{C\in\cl{C}}\trm{rot}_{C}(X) \ = \ \chi(\Sigma)
	\end{equation*}
	where $\chi$ is the euler characteristic.
\end{thm}
heuristic: $\fa X$ VF, sth abt how it behaves near 0's + sth abt how it behaves
at $\p\Sigma$ = topological invariant.

the euler characteristic has many defns. for instance:
\begin{equation*}
	\chi(M) \ = \ \sum_{i=0}^{m}(-1)^{i}\trm{dim}(H^{i}(M))
\end{equation*}
we take an axiomatic route.

\begin{defn}
	the euler characteristic is a fn (for cpt surfaces) that satisfies:
	\begin{enumerate}[E1)]
		\item if $\Sigma=\Sigma'\sqcup\Sigma''$, then $\chi(\Sigma)=\chi(\Sigma')+\chi(\Sigma'')$
		\item if $\Sigma$ obtained from $\Sigma'$ by gluing two $\p$ circles, then
			$\chi(\Sigma)=\chi(\Sigma')$
		\item $\chi(D^{2})=1$
	\end{enumerate}
\end{defn} \

\begin{xmp}
	since $S^{2}=D^{2}\cup_{\p}D^{2}$, $\chi(S^{2})=2$.
\end{xmp} \

\begin{crll}[title=Hairy Ball Theorem]
	every VF on $S^{2}$ has a zero
\end{crll}

\lecdate{Lec 23 - Apr 02 (Week 12)}
fact that was forgotten last time:
given a cpt orient surface w genus $g$ and $r$ bdry circles (think sliced torus),
$\chi(\Sigma)=2-2g-r$.

consider first a VF on $D^{2}$, $X_{p}=f(p)\p_{x}+g(p)\p_{y}$.
we identify it as $F_{X}=(f,g):D^{2}\gto\bR^{2}$.
if $\gamma$ a loop on $D^{2}$ st $X_{p}\neq0$ on $\gamma$, then
we can define:
\begin{equation*}
	\trm{rot}_{\gamma}(X) \ = \ w(F_{X}\circ\gamma)
\end{equation*}
note that if $\gamma$ goes through a zero, it can be deformed arnd it such that
the rot stays the same (by stokes).

given an isolated 0 $p$ of $X$, then any curve $\gamma$ in nonzero nbhd $B$ of $p$
w winding num 1 arnd $p$ has the same rot num.

\begin{defn}
	$\trm{index}_{p}(X)=\trm{rot}_{\gamma}(X)$ for any such $\gamma$ as above.
\end{defn} \

\begin{exr}
	this doesn't depend on choice of chart
\end{exr}

next, we consider rot num along a bdry circle.
note that we can always get a VF $X_{1}$ tangent to a circle $C$,
and if $C$ is a $\p$ circle, we can defn $X_{2}$ as facing ``inward".
then any other VF $X$ along $C$ can be written as:
\begin{equation*}
	X_{p} \ = \ f(p)(X_{1})_{p}+g(p)(X_{2})_{p}
\end{equation*}
so we can define:
\begin{equation*}
	\trm{rot}_{C}(X) \ = \ w(F_{X}\circ\gamma)
\end{equation*}
where $\gamma$ is a parametrization of $C$, and $F_{X}=(f,g):C\gto\bR^{2}$ as before.

\textbf{proof sketch of poincar\'e}:
general strat is to prove LHS satisfies axioms for $\chi$, then invoke uniqueness.
\begin{enumerate}[E1)]
	\item get this man a true (i wasnt paying attn)
	\item $X$ agrees on the two circles since ``inward" vec fields are opposite,
		so rot nums cancel
	\item by additivity of winding num, we can join loops arnd zeroes to get a curve
		$\gamma$, so $\trm{rot}_{\gamma}(X)=\sum_{p}\trm{index}_{p}(X)=\trm{rot}_{\p D^{2}}(X)=\trm{rot}_{C}(X)-1$
		wrt the usual basis, thus LHS is 1.
\end{enumerate}
and thats all folks!
