\subsection{Preliminaries and Initial Definitions}
\lecdate{Lec 1 - May 7 (Week 1)}

\begin{defn}
    $f:\bR\sto\bR$ cts iff $\forall \, x_{0}\in\bR\forall \, \ep>0
    \exists \, \delta>0 \forall \, x\in\bR$ such that:
    \begin{equation*}
        \abs{x-x_{0}}<\delta\implies\abs{f(x)-f(x_{0})}<\ep
    \end{equation*}
    for metric spaces: replace $\bR$ with $X$ in the above, then:
    \begin{equation*}
        d_{X}(x,x_{0})<\delta\implies d_{Y}(f(x),f(x_{0}))<\ep
    \end{equation*}
\end{defn}
damn that spacing sucks. anyway these are defns we're alr familiar with, i.e.
metrics on a set (symmetry, posdef, triangle).
note we call the 2-norm on $\bR^{n}$ as $d_{2}$, or the euclidean metric

note homeos (as we know them intuitively; donut/mug) dont preserve distances.
new goal: define continuity w/o using a metric.

\begin{defn}
    $\cl{T}'$ is finer than $\cl{T}$ iff $\cl{T}\subseteq\cl{T}'$
\end{defn}
no im not paying attn, how could u tell

\newpage
\lecdate{Lec 3 - May 14 (Week 2)}
lol. lmao.

\begin{xmp}[source=Primary Source Material,title=Sorgenfrey Line]
    on $\bR$, consider the collection:
    \begin{equation*}
        \cl{B}_{\ell} := \set{[a,b) \trm{ bounded intervals}}
    \end{equation*}
    $\cl{B}_{\ell}$ is a basis for the \textbf{lower limit topology} on $\bR$.
    the space $\bR_{\ell}:=(\bR,\cl{T}_{\ell})$ is called the Sorgenfrey line.
\end{xmp}

checking basis is easy. $\cl{T}_{\ell}$ is strictly finer than the std topo,
also easy to check.
$\bR_{\ell}$ is \textit{not} 2nd ctbl; taking $\cl{B}=\set{[a,b):a,b\in\bQ}$
generates a different topology than $\cl{T}_{\ell}$.

\begin{prop}
    $\bR_{\ell}$ is not 2nd ctbl
\end{prop}

\begin{pf}[source=Primary Source Material]
    fix a basis $\cl{B}$.
    for any $x$, consider $U_{x}:=[x,x+1)$.
    since $\cl{B}$ a basis, then there exists $x\in B_{x}\subseteq U_{x}$.
    we claim $x\mto B_{x}$ is inj.

    if wlog $x<y$, then $x \notin U_{y}$, so $x \notin B_{y}$.
    since $x\in B_{x}, B_{x}\neq B_{y}$.
\end{pf}

defn: subsptop, prodtop

\lecdate{Lec 6 - May 28 (Week 4)}

\vspace{-0.1in}
\begin{prop}[type=Title,title=Pasting Lemma]
    sps $X=A\sqcup B$, with $A,B$ closed.
    let $f:A\sto Y,g:B\sto Y$ cts, and $f=g$ on $A\cap B$.
    then $h:X\sto Y$ is cts, where:
    \begin{equation*}
        h(x)=
        \begin{cases}
            f(x) & x\in A \\
            g(x) & x\in B
        \end{cases}
    \end{equation*}
\end{prop}



