\subsection{Fourier Series}

recall that a trig poly is a fn of the form:
\begin{equation*}
	f(x) \ = \ b_{0}+\sum_{k=1}^{N}b_{k}\cos(kx)+\sum_{k=1}^{N}a_{k}\sin(kx)
\end{equation*}
we previously showed these can approx $2\pi$-periodic cts fn's, but this was non-constructive.
now, we aim for an explicit approximation.
we'll modify our setup and consider:
\begin{equation*}
	f(x) \ = \ \sum_{k=-N}^{N}c_{k}e^{ikx}
\end{equation*}
where $c_{k}\in\bC$.
if $a_{k},b_{k}$ are complex, these forms become equivalent.
furthermore, $f$ is real iff $c_{k}=\bar{c_{-k}}$
(i think? his notations weird).
recall (sure man):
\begin{equation*}
	\frac{1}{2\pi}\int_{-\pi}^{\pi}e^{ikx}\di x \ = \
	\begin{cases}
		1 & k=0 \\ 0 & k\neq0
	\end{cases}
\end{equation*}
thus, if $f$ is of the above form, then:
\begin{equation*}
	c_{k} \ = \ \frac{1}{2\pi}\int_{-\pi}^{\pi}f(x)e^{-ikx}\di x
\end{equation*}
in particular, for any riemann int'bl $f:[-\pi,\pi]\gto\bC$, we defn:
\begin{equation*}
	\hat{f}(k) \ := \ c_{k} = \frac{1}{2\pi}\int_{-\pi}^{\pi}f(x)e^{-ikx}\di x
\end{equation*}
and ask whether the series:
\begin{equation*}
	\sum_{k}c_{k}e^{ikx}
\end{equation*}
cvgs to $f$ in some sense.
this is the content of this section.

\begin{defn}
	inner product lol. map $\ang{\cdot,\cdot}:V\times V\gto\bC$ with:
	\begin{enumerate}[i)]
		\item $\ang{u,v}=\bar{\ang{v,u}}$
		\item $\ang{u+v,w}=\ang{u,w}+\ang{v,w}$
		\item $\ang{u,\alpha v}=\ang{\bar{\alpha}u,v}=\alpha\ang{u,v}$
		\item $\ang{v,v}\geq0$ w equality iff $v=0$
	\end{enumerate}
\end{defn}
this defns a norm $\norm{f}=\ang{f,f}^{1/2}$.
taking $V=C[a,b]$ over \textit{complex} fn's, we consider:
\begin{equation*}
	\ang{f,g} \ := \ \int_{a}^{b}\bar{f(x)}g(x)\di x
\end{equation*}
this is \textit{almost} an inn prod, but fails iv) (idt it does..? but sure).
however, thats not important for what we want.
we'll henceforth call $\norm{f}=\ang{f,f}^{1/2}$ for this section.

\begin{defn}
	a seq of riemann int'bl fn's $\psi_{n}:[a,b]\gto\bC$ is called \textbf{orthogonal}
	if $\psi_{n},\psi_{m}$ are ortho for $n\neq m$.
	we say they are \textbf{orthonormal} if... well yk.
\end{defn}
eg, taking $[a,b]=[-\pi,\pi]$, $\phi_{n}=\frac{e^{inx}}{\sqrt{2\pi}}$ is
orthonormal.

\begin{defn}
	sps $\phi_{n}$ orthonormal. for riemann int'bl $f$, defn:
	\begin{equation*}
		P_{N}f \ := \ \sum_{j=1}^{N}\phi_{j}\ang{\phi_{j},f}
	\end{equation*}
	clearly $P_{N}(\alpha f+g)=\alpha P_{N}f+P_{N}g$, so $P_{N}$ is in fact a lin op.
\end{defn}
we show it is the ortho proj onto the span of $\set{\phi_{1},\dots,\phi_{N}}$.

\begin{lm} \vspace{-0.2in}
	\begin{enumerate}[i)]
		\item $P^{2}_{N}f=P_{N}f$
		\item $\fa f,g$, we have:
			\begin{equation*}
				\ang{P_{N}f,g} \ = \ \ang{f,P_{N}g} \ = \
				\sum_{j=1}^{N}\ang{f,\phi_{j}}\ang{\phi_{j},g}
			\end{equation*}
			in particular, $P_{N}$ is self-adj.
	\end{enumerate}
\end{lm} \

\begin{pf} \vspace{-0.2in}
	\begin{enumerate}[i)]
		\item since $\phi_{j}$ orthonorm, note $P_{N}\phi_{j}=\phi_{j}$. then:
			\begin{equation*}
				P_{N}P_{N}f
				\ = \ P_{N}\sum_{j=1}^{N}\phi_{j}\ang{\phi_{j},f}
				\ = \ \sum_{j=1}^{N}\ang{\phi_{j},f}P_{N}\phi_{j}
				\ = \ \sum_{j=1}^{N}\ang{\phi_{j},f}\phi_{j}
				\ = \ P_{N}f
			\end{equation*}
		\item by linearity:
			\begin{equation*}
				\ang{P_{N}f,g}
				\ = \ \ang{\sum_{j=1}^{N}\phi_{j}\ang{\phi_{j},f},g}
				\ = \ \sum_{j=1}^{N}\ang{f,\phi_{j}}\ang{\phi_{j},g}
			\end{equation*}
			it is easy to show this is equal to $\ang{f,P_{N}g}$.
	\end{enumerate}
\end{pf} \

\begin{crll} \vspace{-0.2in}
	\begin{enumerate}[i)]
		\item $\norm{P_{N}f}^{2}=\sum_{j=1}^{N}\abs{\ang{\phi_{j},f}}^{2}$
		\item $\ang{P_{N}f,(1-P_{N})g}=0$ for all $f,g$
	\end{enumerate}
\end{crll} \

\begin{thm}
	sps $f:[a,b]\gto\bC$ riemann int'bl and $\phi_{j}$ orthonorm.
	let $c_{k}=\ang{\phi_{k},f}$ and $g_{N}$ a fn of the form:
	\begin{equation*}
		g_{N} \ = \ \sum_{k=1}^{N}a_{k}\phi_{k}
	\end{equation*}
	for $a_{k}\in\bC$. then:
	\begin{enumerate}[i)]
		\item $\norm{f-P_{N}f}\leq\norm{f-g_{N}}$ w equality iff $a_{k}=c_{k}$
		\item we have:
			\begin{equation*}
				\norm{f}^{2}-\norm{f-g_{N}}
				\ \leq \ \sum_{j=1}^{N}\abs{c_{j}}^{2} \ \leq \ \norm{f}^{2}
			\end{equation*}
	\end{enumerate}
\end{thm} \

\begin{pf}
	note $P_{N}g_{N}=g_{N}$.
	\begin{enumerate}[i)]
		\item note:
			\begin{align*}
				\norm{f-g_{N}}^{2}
				& \ = \ \ang{f-g_{N},f-g_{N}} \\
				& \ = \ \ang{f-P_{N}f+P_{N}f-g_{N},f-P_{N}f+P_{N}f-g_{N}} \\
				& \ = \ \ang{f-P_{N}f,f-P_{N}f} + \ang{f-P_{N}f,P_{N}f-g_{N}} \\
				& \ + \ \ang{P_{N}f-g_{N}f,f-P_{N}f} + \ang{P_{N}f-g_{N},P_{N}f-g_{N}}
			\end{align*}
		by cor 7.5 above, this is equal to:
		\begin{align*}
			\norm{f-g_{N}}^{2} & \ = \ \ang{f-P_{N}f,f-P_{N}f}+\ang{P_{N}f-g_{N},P_{N}f-g_{N}} \\
			& \ = \ \norm{f-P_{N}f}^{2} + \sum_{j=1}^{N}\abs{a_{j}-c_{j}}^{2} \tag*{(*)}
		\end{align*}

	\item notice:
		\begin{align*}
			\norm{f-P_{N}f}^{2}
			& \ = \ \ang{f-P_{N}f,f-P_{N}f} \\
			& \ = \ \ang{f,f}-\ang{P_{N}f,f}-\ang{f,P_{N}f}+\ang{P_{N}f,P_{N}f} \\
			& \ = \ \ang{f,f}-\ang{P_{N}f,P_{N}f} \\
			& \ = \ \norm{f}^{2}-\norm{P_{N}f}^{2}
		\end{align*}
		since $P_{N}^{2}=P_{N}$ and it is self-adj. thus:
		\begin{equation*}
			\norm{f-P_{N}f}^{2} \ = \ \norm{f}^{2} - \sum_{j=1}^{N}\abs{c_{j}}^{2}
			\ \geq \ 0 \tag*{(**)}
		\end{equation*}
		this gives the 2nd ineq.
		combining (*) and (**), we get:
		\begin{equation*}
			\norm{f-g_{N}}^{2} \ = \ \norm{f}^{2}-\sum_{j=1}^{N}\abs{c_{j}}^{2}+\sum_{j=1}^{N}\abs{a_{j}-c_{j}}^{2}
			\ \leq \ \norm{f}^{2} - \sum_{j=1}^{N}\abs{c_{j}}^{2}
		\end{equation*}
		giving us the first ineq.
	\end{enumerate}
\end{pf}

\lecdate{Lec 14 - Mar 3 (Week 8)}
wrote this parts notes early thinking i missed it. guess not lol

we now examine applications to fourier series.
in particular, consider the case that $\phi_{n}=\frac{e^{inx}}{\sqrt{2\pi}}$, and:
\begin{equation*}
	P_{N}f \ = \ \sum_{n=-N}^{N}\phi_{n}\ang{\phi_{n},f}
\end{equation*}
note we have to track factors of $2\pi$. if we defn:
\begin{equation*}
	\hat{f}(n) \ := \ \frac{1}{2\pi}\int_{-\pi}^{\pi}f(x)e^{-inx}\di x
\end{equation*}
then the fourier series assoc. to $f$ is written as:
\begin{equation*}
	\sum_{n}\hat{f}(n)e^{inx} \ = \ \sum_{n}\phi_{n}\ang{\phi_{n},f}
\end{equation*}
so $\hat{f}(n)=\frac{\ang{\phi_{n},f}}{\sqrt{2\pi}}$.

\begin{thm}[title=Parseval/Plancherel]
	sps $f:[-\pi,\pi]\gto\bC$ riemann int'bl. then:
	\begin{enumerate}[i)]
		\item $\lim_{N\sto\infty}\norm{f-P_{N}f}=0$
		\item we have:
			\begin{equation*}
				\norm{f}^{2} \ = \ \sum_{\bZ}\abs{\ang{\phi_{n},f}}^{2}
				\ = \ 2\pi\sum_{n}\abs{\hat{f}(n)}^{2}
				\ = \ \left(\int_{-\pi}^{\pi}\abs{f(x)}^{2}\di x\right)
			\end{equation*}
	\end{enumerate}
\end{thm}
[he wrote last one in class; not sure if acc the same.]
we'll need the following lemma:
\begin{lm}
	he changed it...?
	\begin{enumerate}[i)]
		\item if $f$ riemann int'bl, $\ep>0$, then
			$\ex g:(-\pi,\pi)\gto\bC$ cts with $g(-\pi)=g(\pi)$ and
			$\norm{f-g}_{2}\leq\ep$.
		\item if $f$ riemann int'bl, $\ep>0$, then
			$\ex g_{N}=\sum_{k=-N}^{N}a_{k}\phi_{k}$ s.t. $\norm{f-g_{N}}_{2}<\ep$.
	\end{enumerate}
\end{lm}
note thm is immediate from ii).

\begin{pf}
	we start by proving ii) assuming i).
	let $\ep>0$. by i), $\ex g$ cts w $g(-\pi)=g(\pi)$ s.t. $\norm{f-g}_{2}<\ep$.
	it suffices to approx $g$ by $\sum_{k=-N}^{N}a_{k}\phi_{k}$.

	by SW, if $h:(-\pi,\pi)\gto\bR$ cts and $h(-\pi)=h(\pi)$, then
	$\ex$ trig poly $p_{N}$:
	\begin{equation*}
		p_{N} \ = \ \sum_{n=1}^{N}a_{n}\cos(nx) + \sum_{n=1}^{N}b_{n}\sin(nx)
	\end{equation*}
	s.t. $\norm{p_{N}-h}_{\infty}<\ep$.
	but then:
	\begin{equation*}
		\int_{-\pi}^{\pi}\abs{p_{N}-h}^{2}\di x \ \leq \ \ep^{2}2\pi
	\end{equation*}
	thus to approx $g$, we approx $\Re$ and $\Im$ parts separately, and note:
	\begin{equation*}
		\sin(x) \ = \ \frac{e^{ix}-e^{-ix}}{2i} \qquad
		\cos(x) \ = \ \frac{e^{ix}+e^{-ix}}{2}
	\end{equation*}
	now, we provide sketch of i).
	by splitting into $\Re$ and $\Im$ parts, then +ve and -ve parts,
	assume $f\geq0$ RI.

	let $\ep>0$.
	since $f$ riemann int'bl, $\ex$ partition $P=\set{t_{0},\dots,t_{n}}$ of $[-\pi,\pi]$ s.t. if:
	\begin{equation*}
		M_{j} \ = \ \sup_{x\in[t_{j-1},t_{j}]}f(x) \qquad
		m_{j} \ = \ \inf_{x\in[t_{j-1},t_{j}]}f(x)
	\end{equation*}
	and:
	\begin{equation*}
		f_{L} \ = \ \sum_{j=1}^{n}m_{j}\chi_{(t_{j-1},t_{j}]} \qquad
		f_{U} \ = \ \sum_{j=1}^{n}M_{j}\chi_{(t_{j-1},t_{j}]}
	\end{equation*}
	then:
	\begin{equation*}
		\int_{a}^{b}\abs{f_{U}-f}\di x \ \leq \ \int_{a}^{b}\abs{f_{U}-f_{L}}\di x \ < \ \ep
	\end{equation*}
	thus we can approx $f_{U}$ by approxing $\chi$ over int'vls by trapezoids.
\end{pf}
ok new stuff. uh. is it? recall:
\begin{equation*}
	\hat{f}(n) \ = \ \frac{1}{2\pi}\int_{-\pi}^{\pi}f(x)e^{-inx}\di x
\end{equation*}
then parseval says:
\begin{equation*}
	\sum_{\abs{k}\leq N}\hat{f}(k)e^{-ikx} \ \gto \ f
\end{equation*}
in mean square norm.

\begin{thm}
	sps $f$ RI and cts at a pt $\theta_{0}\in[-\pi,\pi]$.
	if $\hat{f}(n)=0 \ \fa n$, then $f(\theta_{0})=0$
\end{thm} \

\begin{pf}
	if $\hat{f}(n)=0$, then $\int_{-\pi}^{\pi}\abs{f(x)}^{2}\di x = 0$.
\end{pf} \

\begin{crll}
	\begin{equation*}
		\sum_{\bZ}\abs{\hat{f}(n)}<\infty \quad \implies \quad
		\sum_{\abs{k}\leq N}\hat{f}(k)e^{-ikx} \ \rightrightarrows \ g
	\end{equation*}
	for some cts $g$.
	if $f$ cts, then $f=g$ on $[-\pi,\pi]$.
\end{crll} \

\begin{pf}
	recall weierstrass $M$-text.
	if $f_{n}$ fn's s.t. $\norm{f_{n}}_{\infty}\leq M_{n}$ with $\sum M_{n}<\infty$, then:
	\begin{equation*}
		\sum_{n=1}^{N}f_{n} \ \rightrightarrows \ F
	\end{equation*}
	for some $F$. the first part thus follows.

	now, let $f_{N}=\sum_{\abs{k}\leq N}\hat{f}(k)e^{ikx}$.
	since $f_{N}\rightrightarrows g$, we know:
	\begin{align*}
		\hat{g}(k) \ = \ \frac{1}{2\pi}\int_{-\pi}^{\pi}g(x)e^{-ikx}\di x
		& \ = \ \frac{1}{2\pi}\int_{-\pi}^{\pi}\lim_{N\sto\infty}f_{N}(x)e^{-ikx}\di x \\
		& \ = \ \lim_{N\sto\infty}\frac{1}{2\pi}\int_{-\pi}^{\pi}f_{N}(x)e^{-ikx}\di x \\
		& \ = \ \hat{f}(k)
	\end{align*}
	thus $\hat{g}(k)=\hat{f}(k)$ for all $k$, so $h=f-g$ cts and
	$\hat{h}(k)=\hat{f}(k)-\hat{g}(k)=0$, so $h=0$.
\end{pf}

\lecdate{Lec 15 - Mar 5 (Week 8)}
sub tdy weeee

oh he switches the order of the inner prod terms:
\begin{equation*}
	\ang{f,g} \ = \ \int_{-\pi}^{\pi}f(x)\bar{g(x)}\di x
\end{equation*}
..? sps $f$ diff'ble, $f'$ int'bl, $f(-\pi)=f(\pi)$. then using IBP:
\begin{align*}
	\hat{f}(k) \ = \ \frac{1}{2\pi}\int_{-\pi}^{\pi}f(x)e^{-ikx}\di x
	& \ = \ \frac{-1}{2\pi}\int_{-\pi}^{\pi}f'(x)\frac{1}{-ik}e^{-ikx}\di x \\
	& \ = \ \frac{1}{ik}\frac{1}{2\pi}\int_{-\pi}^{\pi}f'(x)e^{-ikx}\di x \\
	& \ = \ \frac{1}{ik}\hat{f}'(k)
\end{align*}
so:
\begin{equation*}
	\hat{f}(k) = \frac{1}{ik}\hat{f}'(k) \ \implies \ k\abs{\hat{f}(k)} = \abs{\hat{f}'(k)}
\end{equation*}
now, sps $f$ is $m$-times diff'ble, $f^{(k)}(-\pi)=f^{(k)}(\pi)$.
doing IBP $m$ times gives:
\begin{equation*}
	\abs{\hat{f}(k)} \ = \ \frac{1}{k^{m}}\abs{\hat{f}^{(m)}(k)} \ \leq \ \frac{C}{k^{m}}
\end{equation*}
where $\abs{\hat{f}^{(m)}}\leq C$.
exercise(?): $\hat{(f')}\sim k\hat{f}$.
