\subsection{Limits of measurable functions}

\begin{prop}
	let $f_{n}:E\gto\bar{\bR}$ a seq of ptwise incresing meas. fns for some
	$E$ meas.
	then $\lim_{n\sto\infty}f_{n}(x)=f(x)$ is meas.
\end{prop} \

\begin{pf}
	for all $c\in\bR$, since $f_{n}$ is ptwise increasing, we have:
	\begin{equation*}
		\set{x:f(x)>c} \ = \ \bigcap_{n=1}^{\infty}\set{x:f_{n}(x)>c}
	\end{equation*}
\end{pf} \

\begin{thm}
	sps $E$ meas., $f_{n}:E\gto\bar{\bR}$ seq of meas. fns.
	the following are also meas.:
	\begin{enumerate}[i)]
		\item $x\mto\sup_{n}f_{n}(x)$
		\item $x\mto\inf_{n}f_{n}(x)$
		\item $x\mto\limsup_{n}f_{n}(x)$
		\item $x\mto\liminf_{n}f_{n}(x)$
		\item $x\mto\lim_{n}f_{n}(x)$, provided this exists $\fa x$
	\end{enumerate}
\end{thm} \

\begin{pf}\vspace{-0.2in}
	\begin{enumerate}[i)]
		\item $\fa c\in\bR$:
			\begin{equation*}
				\set{x:\sup_{n}f_{n}(x)>c} \ = \ \bigcup_{n=1}^{\infty}\set{x:f_{n}(x)>c}
			\end{equation*}
		\item similar as above
		\item recall $\limsup_{n}f_{n}(x)=\lim_{n}\set{\sup_{m\geq n}f_{m}(x)}$.
			this is a decreasing seq of meas. fns, so by i), we're done
		\item similar as above
		\item if the lim exists, its equal to both limsup and liminf
	\end{enumerate}
\end{pf}

we know what a.e. is (uses outer meas. specifically, since we dk
a priori the set is meas)

\begin{lm}
	sps $f:\bR\gto\bar{\bR}$ LM and $g:\bR\gto\bar{\bR}$ is s.t. $f(x)=g(x)$ ae.
	then $g$ meas.
\end{lm} \

\begin{pf}
	let $E=\set{x:f(x)\neq g(x)}$.
	for $A\in\cl{B}(\bar{\bR})$, we have:
	\begin{equation*}
		g^{-1}(A) \ = \ (f^{-1}(A)\cap E^{c}) \cup F
	\end{equation*}
	where $F=g^{-1}(A)\cap E$.
	then $m^{*}(F)\leq m^{*}(E)=0$, so $F\in\cl{E}$.
	by assumption, $f^{-1}(A)\in\cl{E}$ and $E^{c}\in\cl{E}$,
	so $g^{-1}(A)\in\cl{E}$.
\end{pf} \

\begin{crll}
	sps $f_{n}:\bR\gto\bar{\bR}$ meas s.t. $\lim_{n}f_{n}(x)$ exists ae.
	let $f(x)=\lim_{n}f_{n}(x)$ when it exists, and arbitrarily otw.
	then $f$ LM.
\end{crll} \

\begin{pf}
	let $E=\set{x:\lim_{n}f_{n}(x) \trm{ exists}}$.
	note $E\in\cl{E}$ since $m^{*}(E^{c})=0$.
	defn:
	\begin{equation*}
		\tilde{f}_{n}(x) \ = \
		\begin{cases} f_{n}(x) & x \in E \\ 0 & \trm{otw} \end{cases}
	\end{equation*}
	then $\tilde{f}(x)=\lim_{n}\tilde{f}_{n}(x)$ exists $\fa \bR$.
	note:
	\begin{enumerate}[i)]
		\item $\tilde{f}_{n}(x)$ LM since $\tilde{f}_{n}=\chi_{E}f_{n}$
		\item $\tilde{f}$ LM since its ptwise lim of LM fns
	\end{enumerate}
	thus $f=\tilde{f}$ a.e., so by lemma, $f$ is LM.
\end{pf} \

\begin{exr}
	show $E$ defn'd as above is always meas., even if the lim
	doesnt necessarily exist ae.
\end{exr}
hint: lim exists iff limsup = liminf.

