\subsection{Path Connectedness and Components}

\begin{prop}
    14.3 + 14.4(def) hold for pconn
\end{prop}

see exercises for pf

\begin{prop}
    pconn implies conn
\end{prop}

\begin{pf}[source=Primary Source Material]
    fix $p\in X$.
    let $B_{q}$ be a path to $q$ for all $q$.
    then $X=\bigcup B_{q}$ is conn as needed.
\end{pf}

\begin{prop}
    components partition $X$
\end{prop}

\begin{pf}[source=Primary Source Material]
    disjoint trivial. for any $x,\set{x}$ conn.
    thus there necessarily is a component containing $x$ for all $x$.
\end{pf}

\begin{prop}
    components closed (subsptop), nonempty conn subset contained in a component
\end{prop}

\begin{pf}[source=Primary Source Material]
    closure of component contains component, second trivial
\end{pf}
note components closed but may not be open

\begin{prop}
    pcomponents partition, are contained in a single component, and
    partition components. pconn subsets contained in a single pcomponent.
\end{prop}
see exr for pf

\begin{defn}
    $X$ \textbf{locally (path-)connected} if it has a basis of open (p)conn
    subsets
\end{defn}

\begin{prop}
    open subset of locally conn is locally conn;
    components of locally conn are open
\end{prop}

\begin{pf}[source=Primary Source Material]
    take basis sets contained in subset.
    for the second, every pt has a conn nbhd;
    by 15.4(b), its contained in the component.
\end{pf}

\begin{prop}
    \vspace{-0.375in}
    \begin{enumerate}[(\alph*)]
        \item locally pconn implies locally conn
        \item open subset of locally pconn is locally pconn
        \item pcomponents of locally pconn are open and equal to components
        \item locally pconn implies conn iff pconn
    \end{enumerate}
    \vspace{-0.1in}
\end{prop}

\begin{pf}[source=Primary Source Material]
    (a) follows from 15.2, (bc) are proved as above and (d) follows from 15.5.
    for (e), conn iff exactly one component iff exactly one pcomponent (by (d))
    iff pconn.
\end{pf}

to summarize, (local) pconn implies (local) conn, and local pconn + conn
implies pconn. exr ?? gives examples for various combinations.

