\subsection{Local Compactness}
amongst metric spaces, the complete ones are particularly nice.
completeness has no meaning topologically, but there is a class of spaces
whose members share many properties as complete metric spaces, and also
contains all mflds - these are the ``locally cpt hausdorff spaces".

\begin{defn}
    a space $X$ is \textbf{locally compact} if $\forall \, p\in X\exists \, $ cpt
    subset containing a nbhd of $p$.
    a subset $A\subseteq X$ is \textbf{precompact} if $\bar{A}$ cpt.
\end{defn}
on its own, this is not particularly useful and does not quite mirror other
``local" defns. it is much more useful, however, when combined w hausdorff.

\begin{prop}
    sps $X$ hausdorff. tfae: \vspace{-0.2in}
    \begin{enumerate}[(\alph*)]
        \item $X$ loc cpt
        \item all pts in $X$ have precpt nbhd
        \item $X$ has basis of precpt open subsets
    \end{enumerate}
\end{prop}

\begin{pf}[source=Primary Source Material]
    clearly (c) imp (b) imp (a), so we show (a) imp (c).
    we show that every pt has nbhd basis of precpt open subsets.
    let $K\subseteq X$ be cpt containing nbhd $U$ of $x$.
    clearly, the collection $\cl{V}$ of all nbhds of $x$ contained in $U$ is
    a nbhd basis of $x$.
    then $K$ closed; if $V\in\cl{V}$, then $\bar{V}\subseteq K$ since
    $V\subseteq U\subseteq K$.
    thus $\bar{V}$ cpt, so take $\cl{V}$.
\end{pf}

\begin{prop}
    every mfld is loc cpt
\end{prop}

\begin{pf}[source=Primary Source Material]
    by 14.18, there is a basis of reg coord balls.
    each is precpt; if the mfld has bdry, it follows from ex ??.18 (18?).
\end{pf}



