\subsection{Product Spaces}
product topology etc etc

\begin{prop}[type=Theorem,title=Characteristic Property of the Product Topology]
    Let $ X = X_{1}\times \cdots \times X_{n} $ be a product space. For any space
    $ Y $, the map $ f:Y \gto X $ is cts iff each $ f_{i} = \pi_{i}\circ f $ cts.
\end{prop}

\begin{pf}[source=Primary Source Material]
    sps each $ f_{i} $ cts. let $ U = U_{1}\times\cdots\times U_{n} $ be a basis
    set. note $ y \in f^{-1}(U) $ iff $ f_{i}(y)\in U_{i} $ for each $ i $, so
    $ f^{-1}(U) = \cap_{i}f_{i}^{-1}(U_{i}) $. each $ f_{i}^{-1}(U_{i}) $ is open
    in $ Y $, so $ f $ cts as needed.

    if $ f $ cts, fix $ i $ and sps $ U \subseteq X_{i} $ open. then
    $ f^{-1}(X_{1}\times\cdots\times U \times\cdots\times X_{n}) $ open in $ Y $,
    but this is just $ f_{i}^{-1}(U) $, so $ f_{i} $ cts.
\end{pf} \

\begin{crll}
    canonical projections are cts
\end{crll}

\newpage
\begin{exr}[source=Primary Source Material]
    prove the above crll using only the characteristic property
\end{exr}

\begin{prop}
    product topology uniquely satisfies the characteristic property, up to
    homeomorphism.
\end{prop}

\begin{pf}[source=Primary Source Material]
    projections are cts by exercise 7.2, and the result follows by applying the
    characteristic property with $ Y $ as the product under the alt topology and
    vice versa
\end{pf}

\begin{prop}
    some properties of the product topology
    \begin{itemize}
        \item fix $ i $. for points $ x_{j} \in X_{j} $ with $ j \neq i $, the
            map $ f:X_{i}\gto X_{1}\times\cdots\times X_{n} $ given by:
            \begin{equation*}
                f(x)=(x_{1},\dots,x_{i-1},x,x_{i+1},\dots,x_{n})
            \end{equation*}
            is an embedding
        \item projection maps are open maps
        \item product of bases is a basis of the product
        \item on a product of subspaces, subspace and product topology are equal
        \item if each $ X_{i} $ is hausdorff/first/second ctbl, so is the product
    \end{itemize}
\end{prop}

see exercise 8.2 for proof. also as a crll, multivalued functions are cts/homeo
iff each component is. anyway, we can apply this to manifolds

\begin{prop}
    given $ M_{1},\dots,M_{k} $ manifolds of dim $ n_{1},\dots,n_{k} $, the
    product $ M_{1}\times\cdots\times M_{k} $ is a manifold of dim $ n_{1}+\dots
    +n_{k} $.
\end{prop}
the pf follows p easy from defns so im omitting it. a useful example is the torus
which we define as follows

\begin{defn}
    we define the $ \bm{n} $\textbf{-torus} as:
    \begin{equation*}
        \bb{T}^{n} \ = \ \underbrace{S^{1}\times\cdots\times S^{1}}_{n
        \trm{ times}}
    \end{equation*}
    interestingly, since $ S^{1} \subseteq \bR^{2} $, we can think of
    $ \bb{T}^{2}\subseteq\bR^{4} $ altho its a surface in $ \bR^{3} $
\end{defn}

