\subsection{Vector Fields}
\lecdate{(check) Lec 13 - Feb 24 (Week 7)}
we jump arnd a bit - doing chs 6/9 kinda together.

whats a vector field? morally, a smooth choice of tangent vec at every pt in $M$.
eg, for $M\subseteq\bR^{n}$, tangent vecs live in $T_{p}M\subseteq\bR^{n}$.

\begin{defn}
	a \textbf{vector field} is a smooth map $X:M\gto\bR^{n}$ s.t.
	$X(p)\in T_{p}M\subseteq\bR^{n}$.
\end{defn}
what does it mean on an abstract mfld? ``lets start by cheating".
v1: look at charts.

\begin{defn}
	a \textbf{vector field} $X$ on $M$ is a map $p\mto X(p)\in T_{p}M$, such that
	for each chart $\vphi$, we have $D_{p}\vphi\circ X:U\gto\bR^{n}$ is smooth.
\end{defn}
this uses the identification $T_{p}M\simeq\bR^{n}$ induced by chart.
but what is that thing between $D_{p}\vphi\circ X$?

\begin{defn}
	the \textbf{tangent bundle} $TM$ of $M^{m}$ is a smooth $2m$-mfld with:
	\begin{itemize}
		\item pt set $\bigsqcup_{p\in M}T_{p}M$
		\item (non-max'l) atlas w charts of the form:
			\begin{equation*}
				\left(\bigsqcup_{p\in U}T_{p}M,(\vphi\circ\pi,D\vphi)\right) \qquad
				(\vphi\circ\pi,D_{p}\vphi):\bigsqcup_{p\in U}T_{p}M\gto\bR^{m}\times\bR^{m}
			\end{equation*}
	\end{itemize}
	for charts $(U,\vphi)$ in $M$.
\end{defn}
check: $\pi$ is smooth. remarks:
\begin{enumerate}[(1)]
	\item the tangent bundle comes w a proj $\pi:TM\gto M$, given by $T_{p}M\mto p$.
	\item for each $p\in M$, the preimg (or fiber) $\pi^{-1}(p)$ is a vspace.
	\item \textit{local triviality:} for each $p\in M$, there's a nbhd $U\ni p$ s.t. the diagram commutes:
		[TODO: add diagram], where $(D\vphi,\pi)$ is a smooth map and
		linear on each $\pi^{-1}(q)$.
\end{enumerate}

\lecdate{Lec 15 - Mar 5 (Week 8)}
accidentally git yeeted tuesdays notes so those are gone forever

last time: a VF $X$ on $M$ defns a flow $\Phi:J\subseteq\bR\times M\gto M$ where $\dot{\Phi}_{t}(p)=X_{\Phi_{t}(p)}$,
for some $J\ni\set{0}\times M$ open.

\begin{defn}
	a VF is \textbf{complete} if $J=\bR\times M$.
\end{defn}
for instance, $x\p_{x}$ is complete w $\Phi_{t}(x)=e^{tx}$, but
$x^{2}\p_{x}$ is not (escapes to $\infty$ in finite time).

\begin{thm}
	if $X$ has cpt sppt, it is complete.
\end{thm} \

\begin{pf} \vspace{-0.2in}
	\begin{enumerate}[1)]
		\item if $p\notin\supp(X)$, $X_{p}=0$ implies $\Phi_{t}(p)=p$ for all $t$.
			if $p\in\supp(X)$, then $\Phi_{t}(p)\in\supp(X)$ when defnd.
		\item since $J$ open, $\fa\ep>0$, there is an open $(-\ep,\ep)\times U_{\ep}$, where:
			\begin{equation*}
				U_{\ep} \ = \ \set{p\in M:\Phi_{t}(p) \trm{ defnd for } t \in (-\ep,\ep)}
			\end{equation*}
			these cvr $M$. by cptness, take finite subcvr $\set{U_{\ep_{i}}}$.
			then $U_{\ep_{\min}}$=M.
		\item by flow property, $\Phi_{\ep_{\min}/2}$ defnd $\fa p\in M$.
			thus $\Phi_{n\ep_{\min}/2}(p)$ is defined on $t\geq0$,
			and $h<0$ can be handled the same way.
	\end{enumerate}
\end{pf}
summary: if $X$ a complete VF, its flow defns a 1-param. family of diffeos.

\begin{crll}
	any VF on a cpt mfld is complete.
\end{crll}
is the crll out of order? oh well. note:
\begin{enumerate}[i)]
	\item $\Phi_{t}\circ\Phi_{s}=\Phi_{t+s}$
	\item $\Phi(t,p)$ is a smooth fn on $\bR\times M$
\end{enumerate}
so $\Phi(t,p)$ a smooth fn on $\bR\times M$.

\begin{prop}
	if $\Phi_{t}$ satisfies i) and ii) above, its the flow of a VF $X$, where:
	\begin{equation*}
		X_{p}(f) \ = \ \frac{\d}{\d t}\bigg\rvert_{t=0}f(\Phi_{t}(p))
	\end{equation*}
\end{prop}
in other words, $X_{p}$ is the vel vec of $\gamma(t)=\Phi_{t}(p)$.

\begin{pf}
	first, $X$ satisfies the product rule:
	\begin{equation*}
		X_{p}(fg) \ = \ \frac{\d}{\d t}\bigg\rvert_{t=0}f(\Phi_{t}(p))g(\Phi_{t}(p))
	\end{equation*}
	its a VF. trust. it is also an integral curve of $X$, as:
	\begin{equation*}
		\dot{\Phi}_{t}(p) \ = \ \frac{\d}{\d s}\bigg\rvert_{s=0}\Phi_{s}(\Phi_{t}(p)) \ = \ X_{\Phi_{t}(p)}
	\end{equation*}
	sure.
\end{pf}

example: given $A\in M_{n}(\bR)$, let $\Phi_{t}:\bR^{m}\gto\bR^{m}$ be:
\begin{equation*}
	\Phi_{t}(x) \ = \ e^{tA}x \ = \ \left(\sum_{n=0}^{\infty}\frac{t^{n}}{n!}A^{n}\right)x
\end{equation*}
then the corresp. VF is:
\begin{equation*}
	X(f)(x) \ = \ \frac{\d}{\d t}\bigg\rvert_{t=0}f(e^{tA}x)
	\ = \ \nabla f\cdot\frac{\d}{\d t}\bigg\rvert_{t=0}e^{tA}x
	\ = \ \nabla f\cdot Ax
\end{equation*}
so in ``wishy-washy physics notation", we have $X=Ax\cdot\nabla$.

now, an alt defn of the lie bracket.
we start with, naturally, the pullback.

\begin{defn}
	given $F:M\gto N$, we denote by $F^{*}f=f\circ F$ the \textbf{pullback} of $f:N\gto\bR$.

	if $F$ is a diffeo, then for a VF $X$ on $N$, we can define $F^{*}X$ by:
	\begin{equation*}
		F^{*}X_{F^{-1}(p)}=TF^{-1}(X_{p})
	\end{equation*}
\end{defn} \

\begin{defn}
	the \textbf{lie derivative} of $f:M\gto\bR$ wrt a VF $X$ is given as:
	\begin{equation*}
		L_{X}f \ = \ \frac{\d}{\d t}\bigg\rvert_{t=0}\Phi_{t}^{*}f \ \in \ C^{\infty}(M)
	\end{equation*}
	the lie derivative of a VF $Y$ wrt $X$ is:
	\begin{equation*}
		L_{X}Y \ = \ \frac{\d}{\d t}\bigg\rvert_{t=0}\Phi_{t}^{*}Y \quad \in \frk{X}(M)
	\end{equation*}
	where $\Phi$ is the flow of $X$.
\end{defn}
check: $L_{X}f=X(f)$.

\begin{thm}
	$L_{X}Y \ = \ [X,Y]$.
\end{thm}

\lecdate{Lec 16 - Mar 10 (Week 9)}
recall the defn of the lie deriv. of a VF.
since $\Phi$ is a diffeo, it induces an isomorphism
$T_{p}M\xrightarrow{ \ T_{p}(\Phi_{t}) \ }T_{\Phi_{t}(p)M}$.
this gives a way to compare vectors in these spaces, as $\Phi_{t}^{*}Y$ pulls
tangent vectors back into $T_{p}M$ (i.e. all vecs $\Phi_{t}^{*}Y\in T_{p}M$).

\begin{pf}[]
	[of 8.10] given $f\in C^{\infty}(M)$, wts $L_{X}Y(f)=[X,Y](f)$. we have:
	\begin{equation*}
		\Phi_{t}^{*}(Y(f)) \ = \ (\Phi_{t}^{*}Y)(\Phi_{t}^{*}f)
	\end{equation*}
	taking deriv at $t=0$, we get:
	\begin{equation*}
		X(Y(f)) \ = \
		\left(\frac{\d}{\d t}\bigg\rvert_{t=0}\Phi_{t}^{*}(Y)\right)(f)
		+ Y(\Phi_{t}^{*}f)
		\ = \ L_{X}Y(f) + Y(X(f))
	\end{equation*}
	thus $L_{X}Y=XY-YX=[X,Y]$ as needed.
\end{pf}
remark: $L_{X}f:=\displaystyle\frac{\d}{\d t}\bigg\rvert_{t=0}\Phi_{t}^{*}f$
measures the change in $f$ along an integral curve(?) of $X$, that is,
a curve whose velocity vector at $t=0$ is $X_{p}$.
this is precisely $X(f)$.
thus, $[X,Y]$ is how $Y$ changes along the flow of $X$.
in particular, we have the following:

\begin{thm}
	sps $\Phi$ flow of $X$, $\Psi$ flow of $Y$. then:
	\begin{equation*}
		[X,Y]=0 \ \iff \ \Phi_{t}^{*}Y = Y \ \iff \ \Psi_{t}^{*}X = X
		\ \iff \ \Phi_{t}\circ\Psi_{s} = \Psi_{s}\circ\Phi_{t}
	\end{equation*}
	for all $s,t$.
\end{thm} \

\begin{pf}
	the first two equivalences are clear from the definition.
	if $\Phi_{t}^{*}(Y)=Y$, then $\Phi_{t}$ takes integral curves of $Y$ to
	integral curves of $Y$. uhm.
	
	he literally just gave up lmao.
\end{pf}
more generally, we have that:
\begin{equation*}
	[X,Y] \ = \ \lim_{t\sto0}\frac{1}{t^{2}}[\Phi_{t}^{*}\Psi_{t}^{*}-\Psi_{t}^{*}\Phi_{t}^{*}]
\end{equation*}
lets not attempt to prove it this time.

and now, an interpretation of the jacobi identity. recall:
\begin{equation*}
	[X,[Y,Z]] + [Y,[Z,X]] + [Z,[X,Y]] \ = \ 0
\end{equation*}
we can rewrite this into the following form (which saany uses):
\begin{equation*}
	[X,[Y,Z]] \ = \ [[X,Y],Z] + [Y,[X,Z]]
\end{equation*}
this can be interpreted as a product rule, where $[\cdot,\cdot]$ is both
the derivation and the product.
``the lie bracket on derivations is a derivation on lie brackets".

a theorem! when can you take lin. indep. VF $X_{1},\dots,X_{r}$ and ``integrate them" to
get an $r$-dim submfld $S$?
i.e., for every $p\in M$, there is locally a unique $r$-dim submfld $S$ thru $p$
s.t. $X_{1},\dots,X_{r}$ are tangent to $S$ near $p$.

\begin{thm}[title=Frobenius' Theorem]
	the above happens iff:
	\begin{equation*}
		[X_{i},X_{j}] \ = \ \sum_{k=1}^{r}c_{ij}^{k}(p)X_{k}
	\end{equation*}
	for all $i,j$. this is called the \textit{frobenius condition}.
\end{thm}
as an example, consider $M=T^{2}$ and $X=2\p_{x}+3\p_{y}$.
representing $T^{2}$ as a quotient of the square, the flow line of $X$ can
be thought of as a line with slope $3/2$.
all of the flow lines is, intuitively, called a \textit{foliation by submflds}.
in particular, the flow lines would ``be" a submanifold.

if on the other hand, we consider $X=\p_{x}+\sqrt{2}\p_{y}$, a single
flow line would densely cover $T^{2}$.
the flow lines also define a foliation, i.e. a locally nice-looking
partition into submflds, but globally they are not submflds.

\begin{lm}[title=Flow-straightening lemma]
	given lin. indep. $X_{1},\dots,X_{r}$ VF on $M$ w $[X_{i},X_{j}]=0$ and
	$p$ s.t. $X_{p}\neq0$, $\ex(U,\vphi)$ near $p$ s.t. $X_{i}=\p_{i}$ wrt the chart.
\end{lm} \

\begin{pf}
	choose a codim $r$ $N$ s.t. $\trm{span}((X_{i})_{p},T_{p}N)=T_{p}M$.
	consider $F:(-\ep,\ep)^{r}\times N\gto M$ given as:
	\begin{equation*}
		F(t_{1},\dots,t_{r},p) \ = \ \Phi_{t_{1}}^{x_{1}}\circ\cdots\circ\Phi_{t_{r}}^{x_{r}}(p)
	\end{equation*}
	note the flows can be rearranged, and we have $TF(\p_{t_{i}})=X_{i}$.
	then $T_{(0,p)}F(s,v)=v+\sum s_{i}(X_{i})_{p}$, so $\Phi$ full rank at $(0,p)$.
	by inv fn thm, we get a chart.
\end{pf}

pf of frebenius thm: forward dir is true since if $X_{i},X_{j}$ are
tangent to submfld $S$, then so is $[X_{i},X_{j}]$.
thus, its in their span.
OTOH, we reduce to $[\cdot,\cdot]=0$ case.
we have (?) in $U\subseteq\bR^{m}$ in coords:
\begin{equation*}
	X_{i}=\sum_{j=1}^{r}a_{ij}(x)\p_{j}+\sum_{j=r+1}^{m}b_{ij}(x)\p_{j}
\end{equation*}
by a lin. change of coords, $a_{ij}(0)=I$ and $b_{ij}(0)=0$.
define $X_{i}=\sum_{j=1}^{r}a_{ij}X'_{j}$.
the $X'_{j}$ span the same thing and commute, so by the lemma,
they give a submfld.
